\documentclass[12pt,a4paper]{article}

\usepackage{times}
%\usepackage{a4paper}

\begin{document}


\section*{Curriculum Vitae -- Ole M{\o}ller Nielsen}

\subsection*{Personal address}
1/16 Watson Street \\
Turner, ACT 2612 \\
Australia \\
+61 (0)2 6262 5779  

\subsection*{Work address}
Computer Sciences Laboratory \\
Research School of Information Science and Engineering \\
Australian National University \\
Canberra, ACT 0200
Australia \\
+61 (0)2 6279 8627 (direct)\\
+61 (0)2 6279 8645 (fax)\\
+61 (0)2 6279 8644 (dept.)
 

%Ole M{\o}ller Nielsen\newline
%{\it UNI$\bullet$C, Danish Computing Centre for Research and Education}\newline 
%{\it Technical University of Denmark, bldg 304}\newline
%{\it 2800 Lyngby, Denmark}\newline
%{\it Tel: +45 35 87 88 89, Fax: +45 35 87 89 90}\newline
%{\it Email: uniomni@uni-c.dk}\newline
%{\it http://www.imm.dtu.dk/\~{}omni}

%\begin{tabbing}
%  xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx\kill
%  Nationality:   \> Danish\\
%  Sex:           \> Male\\
%  Date of birth: \> 27 June 1962\\
%%  Education:     \> M.Sc.\ Mathematics and Computer Science\\
%%                 \> Ph.D.\ Applied Mathematics, Scientific Computing\\
%  Languages:     \> Danish, English, German\\
%\end{tabbing} 


\subsection*{Education}

\begin{itemize}
\item Doctor of Philosophy (May 1998) \\
{\bf Technical University of Denmark} \\ 
Department of Mathematical Modelling  \\
Thesis: ``Wavelets in Scientific Computing''\\ 
Grade Point Average: 11.0/13    %All 11's + one A

\item  Master of Science (November 1993) \\
{\bf Roskilde University, Denmark} \\
Department of Computer Science \\ 
Thesis: ``DISCO -- DIScrete and COntinuous simulation''\\ 
Grade Point Average: 11.4/13  %(10.5 + 12 + 11 + 12)/4

\item  Batchelor of Science (June 1990) \\
{\bf Roskilde University, Denmark} \\
Department of Mathematics \\ 
Grade Point Average: 11.5/13  %(10+13)/2
\end{itemize}

\newpage
\subsection*{Professional Experience}

\begin{itemize}
\item {\em Nov 1998 -- present}: Visiting Fellow (Post Doc) \\
      Computer Sciences Laboratory, RSISE, Australian National University.\\ 
      Research in Wavelets and Data Mining.

\item {\em Mar 1998 -- Oct 1998}: Scientific Computing Consultant \\
      UNI$\bullet$C, Danish Computing Centre for Research and Education.\\
      Development of parallel image analysis algorithm.

%\item {\em Spring 1998}: Teaching assistant \\ 
%      Department of mathematical Modelling, Technical University of Denmark. 
%%     \\ Supervising a student project on wavelet analysis.

\item {\em 20 July -- 31 July 1997}: Visiting graduate student \\
      Computer Sciences Laboratory, RSISE, Australian National University. 

\item {\em 1 June -- 20 July 1997}: Honorary research fellow \\
      Department of Physics, Auckland University, New Zealand.
      % \\ Working with Professor Lionel Watkins, 

\item {\em Jan 1996 -- July 1996}: Visiting graduate student\\ 
      Courant Institute of Mathematical Sciences, New York University. 

\item {\em June 1995 -- Dec 1995}: Visiting graduate student\\ 
      Computer Sciences Laboratory, RSISE, Australian National University.
      % Working with Professor Markus Hegland, 

\item {\em Spring 1995}: Teaching assistant, graduate level, masters course\\
      Technical University of Denmark. \\
      Finite element methods for solving PDE's. 

\item {\em Fall 1997}: Teaching assistant, graduate level, masters course\\ 
      Technical University of Denmark. \\
      Image restauration, multigrid methods, and parallel programming.

\item {\em Jan 1990 -- June 1990}. Teaching assistant, undergraduate level \\
      Roskilde University, Denmark. \\ 
      Supervising student projects. 

\item {\em 1988 -- 1991 (8 semesters)}: Teaching assistant, undergraduate level \\ 
      Department of Computer Science, Roskilde University, Denmark. \\
      Planning and teaching courses in object oriented programming. 
\end{itemize}

\newpage
\subsection*{Ph.D.\ dissertation}

My Ph.D.\ dissertation entitled ''Wavelets in Scientific Computing'' 
was defended May 13 1998 and concerns wavelet analysis, a
relatively new mathematical discipline that has already been widely accepted
in signal processing, e.g.\ for purposes such as image
compression. The crucial feature of wavelets is their ability to represent
different parts of a function at different scales. This leads to sparse
representations of piecewise smooth functions with local oscillations,
singularities or jumps in one of its derivatives.

The objective has been to exploit this property in studying algorithms for
solving partial differential equations. These are applied to the model
problem of light pulse propagation in optical fibers described by the
nonlinear Schr{\"o}dinger equation. I have concentrated on two different
approaches for solving this problem. The first is a Galerkin method, where
the unknown complex field is expanded in a wavelet basis. The linear
differential operator is applied in the space of wavelet coefficients and
the nonlinearity is treated via transformations to and from physical space.
The second approach is based on finite differences on an irregular grid
which is generated from the wavelet coefficients of the complex field. In
this approach both linear and nonlinear parts are treated in the physical
space.

An important aspect of this project has been efficient parallel
implementations of the Fast Wavelet Transform. Much of this work has been
done in collaboration with Professor Markus Hegland, Computer Science
Laboratory, RSISE, Australian National University.

My thesis advisors were Professor Vincent Allan Barker, Professor Per
Christian Hansen, and Professor Mads Peter S{\o}rensen all affiliated to
Department of Mathematical Modelling, Technical University, Denmark.

\subsection*{Lectures and presentations given}

\begin{itemize}
\item ``ANZIAM'99 The 35th Applied Mathematics Conference'', Mollymook, NSW, Australia, 7--11 Feb\ 1999.
\item ``Numerical Methods for Large Scale Systems of Equations'', CMA, Australian National University, 16--20 Nov\ 1998.
\item Lecture on Architecture and Algorithms for Vector Computers at a graduate course, Department of Mathematical Modellings, Technical University of Denmark, 15 September 1998. 
\item ``Second IMA Symposium on Parallel Computation'', St Catherine's College, Oxford, UK, 13 July\ 1998.
\item ``PARA 98'', Umeaa University, Sweden, 14--17 June\ 1998.
\item Lecture on Wavelets and Numerical Analysis at a graduate course,
Department of Mathematical Modellings, Technical University of Denmark, 4 May\ 1998.
\item ``One Day Workshop on Basic Parallel Numerical Algorithms and Their Applications'', UNI$\bullet $C, Denmark, 3 December\ 1997.
\item Seminar at UNI$\bullet$C, Denmark, 24 October\ 1997.  %Parallel Wavelet transforms (Fujitsu)            
\item ``Nordic Graduate Student Workshop in Computational Science and Engineering'', Link{\"o}bing University, Sweden, 29 September -- 1 October\ 1997.
\item  Seminar at CSL, Australian National University, 23 July\ 1997.         %"Wavelets and PDEs"
\item  Seminar at Department of Physics, Auckland university, 11 June\ 1997.  %"Wavelet Tutorial"  
\item  ``DCAMM sixth internal symposium'', Hotel Ebeltoft, Denmark, 17--19 March\ 1997.
\item  Seminar at MIDIT, Technical University of Denmark, 6 March\ 1997.
\item  Seminar at Department of Mathematics, Roskilde University, Denmark, 27 February\ 1997.
\item  Two lectures on Wavelets and Data fitting at a graduate course,
Department of Mathematical Modellings, Technical University of Denmark, 29 October and 1 November 1996.
\item  Seminar at IBM, Yorktown heights, 27 March\ 1996.
\item  Seminar at CSL, Australian National University. November\ 1995.
\item  ``Anziam Graduate Student Seminar day'', Australian Defense Force Academy, University of New South Wales, Australia, 13 October\ 1995. %, 11am-4pm. 
\item  Lecture on Parallel Fast Fourier Transforms at a graduate course,
Department of Mathematical Modellings, Technical University of Denmark, May\ 1995.
\end{itemize}

\subsection*{Other conferences and meetings attended}

\begin{itemize}
%\item  
%  \item  - "Programming on the IBM RS/6000 SP". UNI-C sep 22,23 1997 
\item  ``Para'96'', Workshop on Parallel Scientific Computing, UNI$\bullet $%
C, Denmark, August 1996.
\item  ``Workshop on wavelets and filter banks'' held Gilbert Strang and
Truong Nguyen at University of south Florida, Tampa, 13--15 January 1996.
\item  ``Wavelets 95'', Wavelets Workshop, Australian National University,
26--29 June 1995. 
%  \item - "Comsol Matlab-seminar", DTU - 25. april 1995  
\item  ``Recent Advances in Numerical Methods for Partial Differential
Equations'' Politecnico di Torino, Italy, 14--16 February, 1995.
\item  ``Parcon'94'', Symposium on New Directions in Parallel and Concurrent
Computing'', New York University, 28 October, 1994.
\item  ``Para'94'', Workshop on Parallel Scientific Computing, UNI$\bullet$C,
Denmark, June 1994.
\item  ``Symposium on Numerical Software'', IFIP Working Group 2.5 and
UNI$\bullet$C, The Danish Computing Centre for Research and Education, Denmark,
October 1993.
\end{itemize}

\subsection*{Publications}

\begin{itemize}
\item  {\it Wavelet Analysis for Power System Transients} Anthony Wayne Galli 
and Ole M{\o }ller Nielsen, IEEE Computer Applications in Power, Volume 12, Number 1, January 1999.

\item  {\it Parallel Wavelet Transform} Ole M{\o }ller Nielsen and Markus
Hegland, Submitted to Parallel Computing, December 1997.

\item  {\it A Scalable Parallel 2D Wavelet Transform Algorithm} 
Ole M{\o }ller Nielsen and Markus Hegland, Technical report, TR-CS-97-21, 
Australian National University, 1997.

\item {\it Wavelets and the Nonlinear Schr{\"o}dinger Equation} 
Vincent A. Barker and Ole M{\o}ller Nielsen.
Proceedings at Sixth International Colloquium on Numerical Analysis and Computer Science with Applications,
Plovdiv, Bulgaria, 1997.

\item  {\it Vector-Parallel Fast Wavelet Transforms} Ole M{\o }ller Nielsen,
Gavin Mercer, and Markus Hegland. Proceedings at Parallel Computing Workshop,
Australian National University, Canberra, Australia, 1997.

\item  {\it Fast {2D} Wavelet Transform of Circulant Matrices} 
Ole M{\o }ller Nielsen, Technical report, IMM-REP-1997-8, Technical University of Denmark, 1997

\item  {\it DISCO - DIScrete and COntinuous Simulation in Turbo Pascal}, Ole
M{\o }ller Nielsen and Mette Olufsen, Masters Thesis (Unpublished),
Department of Computer Science, Roskilde University, Denmark, 1993.

\item  {\it Electron Diffusion in Silicium, A Mathematical Model} Ole M{\o}ller Nielsen, Mette Olufsen, Karen Birkelund, and
Jesper Voetmann, Text 231 A+B, IMFUFA, Roskilde University, Denmark, 1991
(In danish).

\item  {\it Automatic diagnosing in digital circuits}, Ole M{\o}ller Nielsen and Bj{\o }rn Christensen, Text 220, IMFUFA,
Roskilde University, Denmark, 1992 (In danish).

\item  {\it RSA - A Cryptographic System}, 
Ole M{\o}ller Nielsen, Mette Olufsen, and Lars Frellesen, Text 187, IMFUFA,
Roskilde University, Denmark, 1990 (In danish).
\end{itemize}

\subsection*{Memberships, Awards and Grants}

\begin{itemize}
\item  SIAM, Society of Industrial and Applied Mathematics, member since
1994.

\item  ``Best Poster Award'' at Nordic Graduate Student Workshop in
Computational Science and Engineering, 29 September\ -- 1 October\ 1997.

\item  ``Travelling Scholarship for Mathematicians'' a danish fellowship
covering all expenses for one year of studies abroad, 1995 -- 1996.

\item  ``Personal Post Doc from the Danish Research Council'' covering
       salary and travelling expenses for post doc position at the ANU, 
       1998 -- 1999.  
\end{itemize}

\subsection*{Services to the Scientific Community}

\begin{itemize} 
  \item Reviewed paper for ``the 4th International Conference on Parallel
  Computation'' (ACPC 99), in Springer Lecture Notes on Computer Science series.
  %http://www.coma.sbg.ac.at/acpc99
  
  \item Chaired session at ``Numerical Methods for Large Scale Systems of Equations'', CMA, Australian National University, 16--20 Nov 1998.
  
  \item Reviewed paper for ``Bulletin of the Australian Mathematical Society'',
  Dec 1998. 
\end{itemize}


\newpage
\subsection*{References}

\noindent Professor Vincent Allan Barker, (vab@imm.dtu.dk)\newline
Department of Mathematical Modelling \newline
Technical University of Denmark, Building 305 \newline
2800 Lyngby, Denmark \newline
Phone: +45 4525 3074 \newline
Fax:\ \ \ \ \  +45 4593 2373\newline

\noindent Professor Per Christian Hansen, (pch@imm.dtu.dk)\newline
Department of Mathematical Modelling \newline
Technical University of Denmark, Building 305 \newline
2800 Lyngby, Denmark \newline
Phone: +45 4525 3097 \newline
Fax:\ \ \ \ \  +45 4593 2373\newline

\noindent Dr Markus Hegland, (Markus.Hegland@anu.edu.au)\newline
Computer Sciences Laboratory, RSISE \newline
Australian National University \newline
Canberra ACT 0200, Australia \newline
Phone: +61 (0)6 279 8648 \newline
Fax:\ \ \ \ \  +61 (0)6 279 8645/8651 \newline

\noindent Professor Stig Andur Pedersen, (sap@ruc.dk)\newline
Department of Mathematics\newline
Roskilde University\newline
Box 260\newline
4000 Roskilde, Denmark\newline
Phone: +45 4674 2265\newline
Fax:\ \ \ \ \  +45 4674 3020\newline

\noindent Dr. Lionel Watkins, (l.watkins@auckland.ac.nz)\newline
Department of Physics\newline
University of Auckland\newline
Private Bag 92019\newline
Auckland, New Zealand\newline
Phone: +64 9 373 7599 - 8878\newline
Fax:\ \ \ \ \  +64 9 373 7445\newline

%\noindent Associate Professor Johnny Ottesen, (johnny@mmf.ruc.dk)\\
%Department of Mathematics\\
%Roskilde University\\
%4000 Roskilde, Denmark\\
%Phone: +45 4674 2298\\
%Fax:   +45 4674 3020\\

\end{document}

