\documentclass[12pt,a4paper]{article}
%\documentclass[12pt]{article}

\usepackage{times}

\pagestyle{empty}

%\textheight=25cm
%\textwidth=15cm 
%\topmargin=-2cm
%\oddsidemargin=0cm

\begin{document}

\begin{center} 
  Ole M{\o}ller Nielsen \\
  133 Limestone Avenue \\
  Braddon, ACT 2612, Australia \\
  P: +61 2 6262 6487,\ \ \ E: Ole.Nielsen@bigfoot.com
\end{center}

\begin{center}
  \hrulefill \\
  {\bf \large Seeking position as developer of  
       scientific software applications.} \\[-0.2cm]
  \hrulefill        
\end{center}



\section*{What can I do for you?}
\begin{itemize} 
  \item Develop a mathematical description of a problem 
  and turn it into efficient sequential or parallel software.  
  \item Analyse performance of algorithms, identify bottlenecks,
  and optimise code for speed and storage requirements.
  \item Communicate the essence of difficult concepts verbally and in writing.
\end{itemize} 


\section*{Some achievements}
\begin{itemize} 
  \item Developed vector-parallel fast wavelet transforms
  for the Fujitsu scientific software library.
  % at the Australian National University.
  %The implementation was accompanied by a performance model that
  %predicted both sequential and parallel actual performance.
  About 80 \% of peak performance on one processor was achieved,
  and the parallel efficiency was {\em independent} of the problem size
  as well as the number of processors. 
  \item Developed an efficient algorithm for 
  wavelet transforms of circulant matrices 
  and various operations on them.
  Exploiting the particular structure of this problem 
  reduced the storage requirements as well as the algorithmic complexity 
  from {\em quadratic} to {\em linear} in the number of non-zeros.
  \item Did the initial analysis, design, and architecture evaluations 
  towards the parallelisation of a medical image analysis algorithm.
  \item Published an easy-to-understand wavelet tutorial
  in IEEE Computer Applications in Power, Volume 12, Number 1, January 1999.
  \item Have given technical and scientific presentations at 
  various institutions including IBM, Yorktown heights (USA); 
  St Catherine's College, Oxford (UK); Umeaa University (Sweden); 
  UNI$\bullet$C (Denmark); and Australian National University (Australia).
\end{itemize} 

\section*{Selected technical skills}
\begin{itemize} 
  \item Programming in C++, Fortran 90, Matlab, and Delphi 
  \item Parallel and distributed computing with MPI and DCOM
  \item Object oriented software development
%  \item Signal processing and data analysis
  \item Technical writing
\end{itemize} 
  
\section*{Some personal qualities}
\begin{itemize} 
  \item Easy going and open minded
  \item High degree of common sense  
  \item Experience with team work
  \item Ambitious but not competitive
\end{itemize}

%
% Fra Christines forslag....
%
%\subsection*{Some personal qualities}
%I am easy going and open minded, 
%have excellent communication skills, am interested in team play,
%can make sound decisions as to when
%  \item 
%  \item Loyal team player%
%  
%\end{itemize}



\section*{Work history and education}
\begin{itemize}
\item {\em Nov 1998 -- present}: Postdoctoral Fellow \\
      Computer Sciences Laboratory, RSISE, Australian National University.\\ 
      Research in Wavelets and Data Mining.
\item {\em Mar 1998 -- Oct 1998}: Scientific Computing Consultant \\
      UNI$\bullet$C, Danish Computing Centre for Research and Education.\\
      Parallelisation of image analysis algorithm.
%  \item PhD in Scientific Computing (1998), \\
%        MS in Computer Science (1993), 
%	BS in Mathematics (1990)
%\end{itemize} %
%%
%
%\newpage
%\subsection*{Education - details}
%\begin{itemize}
\item {\bf Doctor of Philosophy (May 1998)} \\
Technical University of Denmark,  
Department of Mathematical Modelling  \\
Thesis: ``Wavelets in Scientific Computing''\\
Available at {\tt www.imm.dtu.dk/\~{}omni/thesis.html} \\ 
Grade Point Average: 11.0/13    %All 11's + one A

\item  {\bf Master of Science (November 1993) in Computer Science} \\
Roskilde University, Denmark, 
Department of Computer Science \\ 
%Thesis: ``DISCO -- DIScrete and COntinuous simulation''\\ 
Grade Point Average: 11.4/13  %(10.5 + 12 + 11 + 12)/4

\item {\bf Batchelor of Science (June 1990) in Mathematics} \\
Roskilde University, Denmark, 
Department of Mathematics \\ 
Grade Point Average: 11.5/13  %(10+13)/2
\end{itemize}

\newpage
\subsection*{Selected publications}
\input{cv_publ.sub}

\subsection*{Memberships, Awards and Grants}
\input{cv_grants.sub}

%\subsection*{Services to the Scientific Community}
%\input{cv_serv.sub}


\newpage
\subsection*{References}

\noindent Dr Markus Hegland, (Markus.Hegland@anu.edu.au)\newline
Computer Sciences Laboratory, RSISE \newline
Australian National University \newline
Canberra ACT 0200, Australia \newline
Phone: +61 2 6279 8648 \newline
Fax:\ \ \ \ \  +61 2 6279 8645/8651 \newline

\noindent Dr Stephen Roberts, (Stephen.Roberts@anu.edu.au)\newline
Computer Sciences Laboratory, RSISE \newline
Australian National University \newline
Canberra ACT 0200, Australia \newline
Phone: +61 2 6279 8634 \newline
Fax:\ \ \ \ \  +61 2 6279 8645 \newline

\noindent Senior Consultant J{\o}rgen Moth, (Jorgen.Moth@uni-c.dk)\newline
UNI$\bullet$C (The Danish Super Computing Centre) \\
%Technical University of Denmark, Building 304 \newline
2800 Lyngby, Denmark \newline
Phone: +45 35 87 88 89 \newline
Fax:\ \ \ \ \  +45 35 87 89 90 \newline

%\noindent Professor Vincent Allan Barker, (vab@imm.dtu.dk)\newline
%Department of Mathematical Modelling \newline
%Technical University of Denmark, Building 305 \newline
%2800 Lyngby, Denmark \newline
%Phone: +45 4525 3074 \newline
%Fax:\ \ \ \ \  +45 4593 2373\newline

\noindent Professor Per Christian Hansen, (pch@imm.dtu.dk)\newline
Department of Mathematical Modelling \newline
Technical University of Denmark, Building 305 \newline
2800 Lyngby, Denmark \newline
Phone: +45 4525 3097 \newline
Fax:\ \ \ \ \  +45 4593 2373\newline


%\noindent Professor Stig Andur Pedersen, (sap@ruc.dk)\newline
%Department of Mathematics\newline
%Roskilde University\newline
%%Box 260\newline
%4000 Roskilde, Denmark\newline
%Phone: +45 4674 2265\newline
%Fax:\ \ \ \ \  +45 4674 3020\newline

\noindent Dr. Lionel Watkins, (l.watkins@auckland.ac.nz)\newline
Department of Physics\newline
University of Auckland\newline
%Private Bag 92019\newline
Auckland, New Zealand\newline
Phone: +64 9 373 7599 - 8878\newline
Fax:\ \ \ \ \  +64 9 373 7445\newline

%\noindent Associate Professor Johnny Ottesen, (johnny@mmf.ruc.dk)\\
%Department of Mathematics\\
%Roskilde University\\
%4000 Roskilde, Denmark\\
%Phone: +45 4674 2298\\
%Fax:   +45 4674 3020\\


\end{document}

