\documentclass[12pt,a4paper]{article}

\usepackage{times}

%\textheight=25cm
%\textwidth=16cm 
%\topmargin=-4cm
\oddsidemargin=0cm

\pagestyle{myheadings}
\markright{OMN - 2000\ \hrulefill\ }

\setcounter{page}{6}

\begin{document}

\section*{Re:00/C17. Response to selection criteria}

\begin{enumerate} 
  \item I hold a PhD in Scientific Computing, an MS in Computer Science,
  and a BS in Mathematics as detailed in the enclosed CV.
 \item My university degrees (BS, MS, PhD) were all aimed at mathematics, 
  computer science and scientific computing. Since then I have been working
  with either research or actual development in these fields. 
  I spent all of 1999 researching predictive modelling 
  and regression based on wavelets and sparse grids. I presented a paper 
  on this work at the CTAC 99 conference held at the ANU
  and a more comprehensive version is in preparation.
  \item During my work as a consultant at UNI$\bullet$C (see CV for details) 
  I did the initial analysis and design of a parallel image analysis
  algorithm for a private company specialising in medical imaging.
  Unfortunately, I had to leave the project before it was finished
  because of my position at the ANU, but I put much effort into 
  transferring the design documents and test programs to 
  my successor and the project has now completed successfully.
  In addition, my recent work in collaboration with CMIS on 
  data mining in pathology has given me some experience in 
  real-world consultancies.
  \item During my work in data mining I have used tools such as
  Python, Matlab/MEX and Mineset and techniques such as the 
  {\em k-means} 
  algorithm for clustering, regression trees for classification,
  and high dimensional smoothing or additive models for
  predictive modelling.
  \item I am fluent in several object-oriented programming 
  languages including C++, Delphi, Python, and Simula and the 
  object-oriented way of thinking was a very important part of my 
  graduate studies.  
  Other programming languages include Matlab, Fortran/Fortran90, C
  and I am very experienced in using the operating systems 
  UNIX/Linux and Windows NT. 
  Moreover, I have done much work with parallel and distributed computing  
  using MPI and DCOM (Windows).
  \item I have always received very good feedback on my communication skills
  be it addressing an auditorium, negotiating on a one to one basis,
  writing reports, memos, or letters.
  All the above has been necessary components of my PhD studies
  and positions held afterwards.
  Furthermore, part of my masters thesis in computer science 
  consisted of writing comprehensive software documentation and
  a full user manual. 
  Roskilde University where I did my graduate studies has adobted 
  a modern education style where most activities are project 
  oriented, problem driven and interdisciplinary. 
  It is very hard obtain a degree from Roskilde University if 
  one doesn't have extensive communication skills and the ability to 
  work in groups. 
  \item Ability to manage demands of a workload involving 
  both research and consultancy commitments as well as
  competing demands and tight deadlines. Having that general 
  ability wood be very good. 
  However, making the right decision when faced with 
  many alternatives can be very difficult and having done it 
  previously is no guarantee
  that it will happen in a future situation. Having said that,
  I think it is fair to say that getting a post graduate degree
  requires good judgement and quite a bit of adaptability.
  In any case I don't hesitate to listen to the opinions of
  my colleagues when faced with a number of competing strategies, 
  nor do I mind offering my opinion to those faced with difficult decisions.
  Regarding the ability to meet deadlines I can give the following example:   
  My 3 year PhD-stipend expired 1 March 1998. This happened to fall
  on a Sunday so I handed in my dissertation Monday the 2 March 1998.
  My former supervisor Per Christian Hansen, 
  former employer J{\o}rgen Moth and current supervisor
  Dr. Markus Hegland will be happy to verify all these matters.
  \item I have no knowledge of SAS or S-PLUS, but being well versed with 
  a great number of tools as mentioned above, I would be able to
  learn them quickly if necessary.
  When the current collaborative pathology project started, 
  I had no knowledge of either Python or SQL. 
  Yet, I had several tools using these languages ready after a few weeks 
  and I applied them successfully throughout the project.
  \item Having spent most of my carrier in academia, my experiences with
  real-world consultancies is limited. However, my work with UNI-C
  and more recently work in collaboration with CMIS has given me a good deal
  of experience, and, more importantly, been satisfying for both me and 
  my employer.
\end{enumerate}   

\end{document}