\documentclass[12pt]{letter}

\pagestyle{empty}
%\pagestyle{myheadings}
%\markright{OMN - 1999\ \hrulefill\ }


\textheight=25cm
%\textwidth=16cm 
\topmargin=-4cm
\oddsidemargin=0cm

\begin{document}

\address{       Dr.\ Ole M{\o}ller Nielsen     \\
                Computer Sciences Laboratory, RSISE   \\
                Australian National University \\
		Canberra, ACT 0200     \\
                Ph: +61 2 6279 8627 \\
                email: Ole.Nielsen@anu.edu.au}


\signature{Ole M{\o}ller Nielsen}

\begin{letter}
{CSIRO Mathematical and Information Sciences, Enterprise Data Mining\\
% Brisbane, Qld \\
 Att: The Personnel Officer}
 
\opening{\underline{Re: 00/C17. Research Scientist - Enterprise Datamining.}}

I write in response to your job advertisement posted to the Data Miners 
Mailing List on 8 March 2000.

I am currently employed as a postdoctoral fellow at the 
Australian National University as a researcher in 
wavelets, data mining, and parallel algorithms.
However, this is a temporary position, and my ambitions
are ultimately to do scientific software development
aimed at concrete applications and motivated by real-world problems.

Also, having worked in collaboration with CMIS for the past three months,
has been interesting, dynamic, challenging, and I have 
enjoyed doing work driven by real demands.
Hence my interest in the position at CMIS.

My main expertises are in development of scientific software
and mathematical modelling.
Aside from an extensive variety of technical skills 
I think of myself as a reliable but easy going team player with 
very good communication skills.

Due to commitments in my present position I will not be available
until 1 October 2000.
Please find enclosed CV and response to the selection criteria. 
I will be happy to provide additional documentation upon request.

\vspace{1cm}
\closing{Best regards}

\end{letter}
\end{document}

