\documentclass[12pt]{letter}

\pagestyle{empty}
%\pagestyle{myheadings}
%\markright{OMN - 1999\ \hrulefill\ }


\textheight=25cm
\textwidth=16cm 
\topmargin=-4cm
\oddsidemargin=0cm

\begin{document}

%\address{       Dr.\ Ole M{\o}ller Nielsen     \\
%                Computer Sciences Laboratory, RSISE   \\
%                Australian National University \\
%		Canberra, ACT 0200     \\
%                Ph: +61 2 6279 8627 \\
%                email: Ole.Nielsen@anu.edu.au}


\signature{Ole M{\o}ller Nielsen}

\begin{letter}
{Australian Computer Society \\
 160 Clarence street \\
 Level 3 \\
 Sydney NSW 2000}
 
\opening{\underline{Application for Skills Assessment.}}


Please find enclosed documents supporting my application for skills
assessment as an IT professional (one of the ASCO codes starting with 2231).
I will need the assessment for an application for skills-based immigration
into Australia.

\begin{enumerate} 
  \item Application form.
  \item Certified copy of Danish passport.
  \item Resume.
  \item Documentation for degrees in computer science and mathematics,\\  
  Roskilde University Centre, Denmark.
  \begin{enumerate} 
    \item Letter from the examination office.
    \item Letter from supervisor.
    \item Certified academic transcripts (Danish).
    \item English translations of the academic transcripts.
  \end{enumerate}
  \item Documentation for Ph.D. in scientific computing, 
  Technical University of Denmark. 
  \begin{enumerate} 
    \item Letter from the examination office.  
    \item Letter from supervisor.
    \item Certified Ph.D. Diploma.
    \item Ph.D. thesis evaluation.
  \end{enumerate}
  \item Reference letter from UNI$\bullet$C, 
  Danish computing centre for research and education.
  \item Reference letter from Computer Science Laboratories, RSISE, 
  Australian National University.
%  \item Reference letter from 
%  Commonwealth Science and Industrial Research Organisation.
\end{enumerate}


\vspace{1cm}
\closing{Best regards}

\end{letter}
\end{document}

