\documentclass[12pt]{letter}

\pagestyle{empty}
%\pagestyle{myheadings}
%\markright{OMN - 1999\ \hrulefill\ }


\textheight=25cm
%\textwidth=16cm 
\topmargin=-4cm
\oddsidemargin=0cm

\begin{document}

\address{       Dr.\ Ole M{\o}ller Nielsen     \\
                Computer Sciences Laboratory, RSISE   \\
                Australian National University \\
		Canberra, ACT 0200     \\
                Ph: +61 2 6279 8627 \\
                email: Ole.Nielsen@anu.edu.au}


\signature{Ole M{\o}ller Nielsen}

\begin{letter}
{CSIRO Tropical Agriculture and CRC for Sustainable Sugar Production\\
% Brisbane, Qld \\
 Att: Dr. Russell Muchow \& Dr. Andrew Higgins}
 
\opening{\underline{Re: ST99--11. Project Officer - Computer Modelling Applications.}}

I write in response to your job advertisement in 
Adelaide university's web listing of statistical
vacancies.

I am currently employed as a postdoctoral fellow at the 
Australian National University as a researcher in 
wavelets, data mining, and parallel algorithms.
However, this is a temporary position, and my ambitions
are ultimately to do scientific software development
aimed at concrete applications and motivated by actual 
demands from society. 
Hence my interest in the position at CSIRO.
%Also, having worked with wavelets for many years in different
%settings I have developed a deep interest in the field of 
%computer graphics and would thus like to gain some experience
%within this exciting area.  

My main expertises are in development of scientific software,
mathematical modelling, and wavelet analysis.
Aside from an extensive variety of technical skills 
I think of myself as a reliable but easy going teamplayer with 
very good communication skills.


Please find enclosed CV and response to the selection criteria. 

\vspace{1cm}
\closing{Best regards}

\end{letter}
\end{document}

