\documentclass[12pt]{letter}

\pagestyle{empty}
%\pagestyle{myheadings}
%\markright{OMN - 1999\ \hrulefill\ }


\textheight=25cm
%\textwidth=16cm 
\topmargin=-4cm
\oddsidemargin=0cm

\begin{document}

\address{       Dr.\ Ole M{\o}ller Nielsen     \\
                Computer Sciences Laboratory, RSISE   \\
                Australian National University \\
                Canberra, ACT 0200     \\
                Ph: +61 2 6279 8627 \\
                email: Ole.Nielsen@anu.edu.au}


\signature{Ole M{\o}ller Nielsen}

\begin{letter}
{Geosciences Australia} 
 
\opening{\underline{Re: RN 02703 --- Software Engineer.}}

I write in response to your job advertisement posted on the WEB 
late August this year for the position as software engineer (no 02703)
under the Risk Modelling Project in the Mineral and Geohazards division.

I am currently working at the Mathematical Sciences Institute as
a research fellow researching data mining, 
data exploration, wavelets and parallel algorithms.
My position is funded by Australian Partnership for Advanced Computing 
(APAC).

However, this is only a temporary research position (3 years),
and my ambitions are ultimately to get more involved with software development
aimed at concrete applications defined by real needs.

In addition to a broad range of technical skills 
my main expertises are in scientific software development,
large scale data analysis, high performance computing, 
and mathematical modelling and I believe I meet all of the selection criteria 
listed in the advertisement.

Please find enclosed CV and response to the selection criteria.
I will be happy to provide additional documentation upon request.

Unfortunately, 
I will be unavailable for interviewing between 
19 September and 14 October 2002.

\vspace{1cm}
\closing{Best regards}

\end{letter}
\end{document}

