\documentclass[12pt,a4paper]{article}

\usepackage{times}

%\textheight=25cm
%\textwidth=16cm 
%\topmargin=-4cm
\oddsidemargin=0cm
\pagestyle{myheadings}
\markright{OMN - 2002\ \hrulefill\ }

%\setcounter{page}{8}

\begin{document}

\section*{EF-PN: 02703 --- Response to selection criteria}

\subsection*{Record of achievement}
\begin{itemize}
  \item \textit{Qualifications}:
  I have a PhD in Scientific Computing, MS in Computer Science,
  and BS in Mathematics as detailed in the enclosed CV.
  I have postdoctoral experience in data mining research and consulting
  from November 1998 to the present.

  During my studies and subsequent appointments I have worked with
  a wide range of topics from computer science and computational mathematics
  including wavelet methods for solving differential equations, 
  special wavelet transforms of circulant matrices, 
  parallel implementations and performance 
  analyses of wavelet transforms and fast Fourier transforms, 
  research in predictive modelling, data mining consultancies, 
  development and application of data exploration software, 
  design and implementation of on-line data analysis on the WEB, 
  efficient use of parallel computers and clusters,
  UNIX systems administration.
  
  I have developed software throughout all of my career
  and am fluent in a large number of 
  (object-oriented) programming languages including
  Python, C++, Matlab, Delphi, and Simula. 
  I am also well experienced in 
  systems analysis, extensible and modular design methodologies, 
  robust and efficient implementations, effective unit testing and debugging, 
  documentation and presentation, as well as application to real-world
  problems and production of end-user programs.
  Examples are a Matlab toolbox for wavelet analysis, 
  Python Toolbox for database exploration with caching, 
  design of an online data analysis WEB application (with CSIRO),  
  Web repository of GPS coordinates with proximity searching,
  Python binding to Message Passing Interface (MPI),
  Automatic, incremental backup of Linux desktops to UNIX file servers. 
  These claims can all be verified by my colleague Dr Peter Christen
  and by visiting http://datamining.anu.edu.au/\~{}ole/software
    
  \item \textit{Achievements implementing complex ideas}: 
    I have been heavily involved in an ongoing collaboration 
    with Center for Mathematics and Information Science at CSIRO
    in joint consultancies for the Health Insurance Commission (HIC)
    and Department for Health and Age Care (HAC). 

    In the most recent collaborative project with CSIRO/CMIS 
    I played a major role in developing
    technologies for online and WEB data exploration to be used 
    by policy makes at the HIC. 
    
    In my current position I am researching and implementing methods 
    for handling the large data sets and high dimensionality 
    encountered in real-life applications. This software takes 
    advantage of high performance parallel computer architectures.
    
    These claims can all be verified by Dr Graham Williams who was 
    supervising the projects at CSIRO
    and Dr Stephen Roberts from my current department.    

  \item \textit{Contribution to team achievements}:
  	During three collaborative projects between the ANU and CSIRO (CMIS)
	I participated in intensive team work with close interactions
	and sometimes under difficult circumstances. All projects came 
	to fruition and I believe my fellow participants will agree
	that I functioned very well in those settings.
	Team members Graham Williams and Peter Christen
	% and team leader Simon Hawkins 
	can confirm that. 

\end{itemize}
  
\subsection*{Evidence of Leadership}
\begin{itemize}
  \item \textit{Experience in assessing project needs}: 
  My under graduate studies at Roskilde University 
  were undertaking in a very modern university
  where half of all study activities were conducted as
  student driven, inter-disciplinary problem-oriented 
  project work in groups. 
  The purpose of this teaching methodology is to 
  prepare students for the realities of a modern working environment.
  This university is a role model for other institutions
  trying to modernise and it is fair to say that nobody graduates from
  Roskilde University without having a solid understanding of the 
  practicalities of project work.
  This can be verified at Roskilde University
  http://www.ruc.dk/ruc\_en/studying/RUC/pw/, by the referee
  referee Dr.\ Johnny Ottesen who were one of my supervisors
  or by Dr.\ Katherine Legge (k.legge@bendigo.latrobe.edu.au, (03) 54447393), 
  La Trope University, Bendigo who have studied the teaching philosophy 
  of Roskilde University in great detail.
  
  \item \textit{Ability to improve existing methods and develop new processes, solutions and innovative techniques to meet client needs.}: 
  I have not yet had a leadership role per se.
  However, working in an ever changing environment, I am constantly facing
  the need to come up with solutions and techniques to meet the needs 
  of collaborators and colleagues.
  One example is a novel smart-caching package I developed in response to
  data mining tasks and later deployed in a very innovative way
  to make a WEB datamining application responsive. Without some sort of
  smart caching it would not have worked at all as many of the computations
  required hours to complete. With caching these results were produced 
  in milliseconds.
  The caching module is available as open source at
  http://datamining.anu.edu.au/\~{}ole/work/software/caching
  and my claims can be verified by Dr Peter Christen. 
  
  %I participated actively in the supervision of a post graduate 
  %summer scholar, Tim Hancock, from December to February this year.
  %He was planning to do postgraduate studies in data mining and had 
  %contacted our group.
  %In addition I have many years of experience in tuition of both 
  %under graduates and post graduates during my own studies.

\end{itemize} 

\subsection*{Evidence of Management}
\begin{itemize} 
  \item \textit{Experience in planning and managing personal and project performance and activities as well as flexibility in dealing with changes in priorities, resources and client requirements.}:
  This is a skill which is necessary in any position 
  (and any PhD study for that matter).
  I would not be where I am without that skill.
  
  \item \textit{Interpersonal communication skills of a high.}: 
  I always get long very well with my colleagues - even if we have differences.
  This can be verified by anyone I have ever worked with.
  
  \item \textit{Understanding of the principles of workplace diversity management and 
  occupational health and safety.}:  
  I understand and respect these principles.
  Making use of different skills and backgrounds in a project can lead to great results if 
  properly recognised and managed; for example by realising that there are always more than 
  one solution to any given problem.
\end{itemize} 
   
\subsection*{Client Interaction}
\begin{itemize} 
  \item \textit{Experience in identifying and meeting client requirements and maintaining client relationships.}:
  I have successfully interacted with people various fields.
  Examples are Michael Fett (Epidemiology and health science)
  where administrative health data was mined for patterns in the 
  treatment of gastro-intestinal diseases, 
  Christopher Zoppou (Hydrology) where 300 Australian rivers were 
  clustered based on wavelet-energy signatures,
  Magaret Kahn (Astronomy and high performance computing)
  where software for exploration of astronomical time-series was enhanced
  performance-wise through the use of a caching mechanism developed by me,
  Anthony Galli (Engineering) where wavelets were applied in 
  electrical engineering.
  
  
  In my current position I cultivate and maintain relationships with several
  collaborators in for example NSW Health and Center for Bioinformatics.
  The former is an ongoing collaboration with Tim Churches in tools and 
  techniques for data mining and the latter is (with Dr Hilary Booth) 
  about statistical methods for scoring protein alignments.
  In collaborations with CSIRO I was exposed to demands from
  paying clients and experienced the need (as uncomfortable as it is)
  for flexibility to make changes especially towards the end of a project.
  
  \item \textit{Willingness and Ability to promote the Project's objectives to clients and maintain ongoing client liaison.}:  
  
  During my work at I have been active in 
  developing research and consultancy collaborations with colleagues 
  within the ANU such as the ANUSF (Margaret Kahn) or DCS (Peter Christen) 
  as well as outside such as 
  CSIRO (Graham Williams, Simon Hawkins, Rohan Baxter, 
  Michael Fett, Christopher Zoppou), 
  National University of Singapore (Zuowei Shen), 
  Siemens Westinghouse (Anthony Galli)
  or lately Tim Churches from the NSW Department of Health who 
  contacted me in response to my participation at the Ninth International 
  Python conference. 

\end{itemize} 

\subsection*{Corporate Contribution}
\begin{itemize} 
  \item \textit{Willingness and Ability to share expertise and to undertake responsibilities beyond immediate work area, and to participate in activities which brings credit to the organisation.}: 

  Within that last few years I have started publishing suitable 
  software on the WEB as open source. Not only does this speed-up the 
  development due to contributions from others. It also gives enormous 
  credit to my home institution whenever it is used.
  See http://datamining.anu.edu.au/\~{}ole/software/
    
\end{itemize}

\subsection*{Other}
\begin{itemize} 
  \item I have been an permanent resident in Australia since March 2001,
  will be eligible for citizenship in March 2003, 
  engaged to an Australian woman,
  and own property in Canberra. 
  However, my home country does not allow dual citizenship, 
  so Australian citizenship would mean giving up my European passport.
  Obviously, I hesitate to do that at this stage.
  %\item Should I be succesful in getting the position at Geosciences Australia   I will be 
  %terminating my contract at the ANU. This will cause some regrettable
  %inconveniencies for my colleagues and 
  %especially for my supervisor Dr Markus Hegland.
\end{itemize} 


\end{document}