\documentclass[12pt]{letter}

\pagestyle{empty}
%\pagestyle{myheadings}
%\markright{OMN - 1999\ \hrulefill\ }


\textheight=25cm
\textwidth=16cm 
\topmargin=-4cm
\oddsidemargin=0cm

\begin{document}

\address{Dr.\ Ole M{\o}ller Nielsen     \\
         Computer Sciences Laboratory, RSISE   \\
         Australian National University \\
         Canberra, ACT 0200}
%                Ph: +61 2 6279 8627 \\
%                email: Ole.Nielsen@anu.edu.au}

\signature{Ole M{\o}ller Nielsen}

\begin{letter}
{Australian Embassy Berlin \\
 Friedrichstrasse 200 \\
 10117 Berlin \\
 Germany}
 
\opening{\underline{Application for Permanent Residency in Australia, 
Skilled -- Independent Migration.}}

Please find enclosed documents supporting my application for skilled
migration to \mbox{Australia} as an IT professional 

\begin{enumerate} 
  \item Contact addresses
  \item Application form
  \item Proof of payment of application fee (AUD 1075)
  \item Certified copy of Danish passport
  \item Skills assessment from the Australian Computer Society (ACS)
  \item Proof of specific work experience in the last 4 years
  \item IELTS language assessment
  \item Proof of health
  \item Resume
  \item Police certificate of good conduct from Denmark
  %\item Four passport photos	
\end{enumerate}

\noindent Re 7: The original IELTS report was sent to you from University 
of Canberra 9/8/2000.

\noindent Re 10: An Australian Police Certificate of good conduct is 
currently being processed and will be provided as soon as it is ready.
The Danish Police certificate was obtained shortly 
before I left for Australia on a 419 visa in November 1998. 
I haven't been back since, so I believe it still reflects my 
character as far as the Danish authorities are concerned.
If you need a newer one, however, please let me know.

\noindent It would be very convenient if any interviews in Berlin 
could be arranged in September 2000 where I will be in Denmark.
From 1 November I will resume my job at the 
Australian National University on a 418 Visa. 
Alternatively, interviews could be conducted in Canberra at a later date.


\closing{Best regards}

\end{letter}
\end{document}

